\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-26 doc/paper.tex
Fixes #179, fixes #180.

	\section{User Study} \label{sec:userstudy} During development, we conducted a
	brief, four-participant user study to detect conflicts between our
	design and the goals in Section \ref{goals}. We designed the study to be
	exploratory; given trees based in the Enron dataset and at least twenty
	minutes, we asked the participants to adopt the persona of a consultant
	evaluating a company's spreadsheet practice, allowing for questions like which
	functions on which the employees most depended or which sheets or employees
	presented the most anomalous or dangerous designs. Though we instructed them on
	how to use the tool and suggested that they visit one of the most populous
	trees in the set, we put aside any specific tasks or questions and let them
	choose their own paths. Though interpretation of the phrase ``spreadsheet
	practice" can certainly vary from participant to participant, we readily
	accepted this interpretive flexibility since we wanted a range of views and
	backgrounds despite the persona. We clarified, furthermore, that their
	observations could be directed either at the quality of the data conveyed by
	the tool or at the tool's design itself. \par

	Nevertheless, these user studies were a formative moment in evaluating the
	tool's performance, generating a number of directions or corrections in the
	process. We present an overview of responses below, with the four participants
	recorded simply as P1 through P4. \par

	\subsection{Use in Smell Tracking} \begin{wrapfigure}{O}{.25\textwidth}
		\centering \includegraphics{SUM}  \caption{An abundance of parameters in SUM.
			Encountering this, P4 remarked, "Woah."} \label{fig:sum} \end{wrapfigure}

@@

@@

	The detection of bad design, however, is certainly not limited to a
	visualization tool, and some users remarked that a tool which printed a list of
	errors could suffice just as well for that purpose. However, they also remarked
	that this visual interface better supports the case when searching for new and
	unknown brands of bad smell. Because the exploratory design makes no
	qualitative judgment and visualizes benign designs with the problematic, it
	therefore allows for flexible interpretation of what is a smell; that is, a
	user might not realize a certain design is suboptimal until they see it in the
	tree and, at the point, find specific examples of where it occurs in the
	spreadsheets.

>>>>

	\section{User Study} \label{sec:userstudy} During development, we conducted a
	brief, four-participant user study to detect conflicts between our
	design and the goals in Section \ref{goals}. We designed the study to be
	exploratory; given trees based in the Enron dataset and at least twenty
	minutes, we asked the participants to adopt the persona of a consultant
	evaluating a company's spreadsheet practice, allowing for questions like which
	functions on which the employees most depended or which sheets or employees
	presented the most anomalous or dangerous designs. Though we instructed them on
	how to use the tool and suggested that they visit one of the most populous
	trees in the set, we put aside any specific tasks or questions and let them
	choose their own paths. Though interpretation of the phrase ``spreadsheet
	practice" can certainly vary from participant to participant, we readily
	accepted this interpretive flexibility since we wanted a range of views and
	backgrounds despite the persona. We clarified, furthermore, that their
	observations could be directed either at the quality of the data conveyed by
	the tool or at the tool's design itself. We present an overview of responses below, with the four participants
	recorded simply as P1 through P4. \par

	\subsection{Use in Smell Tracking}

@@

	\begin{wrapfigure}{O}{.25\textwidth}
		\centering \includegraphics{SUM}  \caption{An abundance of parameters in SUM.
			Encountering this, P4 remarked, "Woah."} \label{fig:sum} \end{wrapfigure}

@@

	The detection of bad design, however, is certainly not limited to a
	visualization tool, and some users remarked that a tool which printed a list of
	errors could suffice just as well for that purpose. However, they also remarked
	that this visual interface better supports the case when searching for new and
	previously unknown smells. Because the exploratory design makes no
	qualitative judgment and visualizes benign designs with the problematic, it
	therefore allows for flexible interpretation of what is a smell; that is, a
	user might not realize a certain design is suboptimal until they see it in the
	tree and, at the point, find specific examples of where it occurs in the
	spreadsheets.
